\speculake: Hiding Malware in Speculative Execution

### 2018-05-09 paper/figures.tex
Expectre payload model figure updates
target fn translated to speculative gadget
add initial turing success comentary

\newcommand{\FigGeneralModel}{
\begin{figure}[t]
    \centering
        \includegraphics[width=0.4\textwidth]{figures/general_model.pdf}
    \caption{ General model of speculative computation within the Payload 
        process when triggered. \textit{Speculative Computation} has read-only
        access to all memory within the process, and returns a result via a
        cache side channel (via the \texttt{probe\_array}).
        The process can subsequently make
        \textit{Resultant Computations} based on the value returned from
        the cache side channel to update the state of the process. }
    \label{fig:general_model}
\end{figure}
}

\newcommand{\FigSpecBandwidth}{
\begin{figure}[t]
    \centering
        \includegraphics[width=0.5\textwidth]{figures/Speculative_bandwidth}
    \caption{Speculative Bandwidth - Using the speculative primitive 
        1KB of data can be decrypted and exfiltrated at a speed between 5 and 6 kbps
        from the speculative world. Varying the width of the channel 
        results in competing performance factors -- decreasing the 
        number of loops vs decreased size of the probe space.}
    \label{fig:spec_bandwidth}
\end{figure}
}

\newcommand{\FigSpasmModel}{
\begin{figure}[b]
    \centering
        \includegraphics[width=0.5\textwidth]{figures/spasm_model.pdf}
    \caption{This model describes the VM control flow. An encrypted SPASM binary 
        stored in dead code or data accessible to \textit{Speculative Computation} 
        is decrypted  and then returned through the primitive. The SPASM 
        \textit{Resultant Computation} performs the SPASM emulation to update the 
        process state before the next instruction is decrypted.}
    \label{fig:spasm_model}
\end{figure}
}

>>>>

\newcommand{\FigGeneralModel}{
\begin{figure}[t]
    \centering
        \includegraphics[width=0.4\textwidth]{figures/general_model.pdf}
    \caption{General model of speculative computation within the Payload 
        process when triggered. \textit{Speculative Computation} has read-only
        access to all memory within the process, and returns a result via a
        cache side channel (via the \texttt{probe\_array}).
        The process can subsequently make
        \textit{Resultant Computations} based on the value returned from
        the cache side channel to update the state of the process. }
    \label{fig:general_model}
\end{figure}
}

\newcommand{\FigSpecBandwidth}{
\begin{figure}[t]
    \centering
        \includegraphics[width=0.5\textwidth]{figures/Speculative_bandwidth}
    \caption{Speculative Bandwidth---Using the speculative primitive 
        1KB of data can be decrypted and exfiltrated at a speed between 5 and 6 kbps
        from the speculative world. Varying the width of the channel 
        results in competing performance factors -- decreasing the 
        number of loops vs decreased size of the probe space.}
    \label{fig:spec_bandwidth}
\end{figure}
}

\newcommand{\FigSpasmModel}{
\begin{figure}[b]
    \centering
        \includegraphics[width=0.46\textwidth]{figures/spasm_model.pdf}
    \caption{This diagram demonstrates the control flow of a \speculake application
        making use of the decryption gadget and emulation. An encrypted SPASM binary 
        stored in dead code or data accessible to \textit{Speculative Computation} 
        is decrypted  and then returned through the primitive. The 
        \textit{Resultant Computation} performs the SPASM emulation to update the 
        process state before the next instruction is decrypted.}
    \label{fig:spasm_model}
\end{figure}
}

\newcommand{\FigTuringSuccess}{
\begin{figure}[t]
    \centering
        \includegraphics[width=0.46\textwidth]{figures/SuccessAndTime}

    \caption{The number of instructions and success rate of a the 5-state Busy 
    Beaver configuration were measured as a function of how many iterations 
    into the speculative world were performed. We see that the amount of time 
    to reach 20,000 instructions completed is a linear function of how many 
    indirect calls into the speculative world we take. Additionally we see that 
    it only requires using 4 speculative calls to achieve no errors in reaching 
    20,000 instructions.}

    \label{fig:turing_success}
\end{figure}
}

### 2018-05-09 paper/implementation.tex
add initial turing success comentary

@@

%In our model the real world keeps track of the Turing state and tape. The
%speculative world uses this information to load a specific value into cache. The
%real world then times the loading of these values to determine which value was
%loaded speculatively. This value is then used to update the state and tape and
%the process is repeated until a halt state is reached.

@@

Our Turing implementation discovered that 50 repetitions is sufficient for
the real world to determine the correct value, as the ``hit rate'' for any one
iteration observing the correct value loaded in cache was over 80\%.

>>>>

\FigTuringSuccess

@@

@@

Our Turing implementation discovered that 4 repetitions is sufficient for the
real world to determine the correct value, as the ``hit rate'' for any one
iteration observing the correct value loaded in cache was over 80\%.
